Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-06-20 demystify.tex
updates

\section{Costly Gifts}\label{sec:gifts} In many countries, it is customary to give professors costly gifts (e.g., expensive liquors, jewelry, or even money), often during the holidays, to show respect and appreciation.  In the US, this is can be considered \emph{inappropriate} and discouraged. Most international students are aware of this, however, they might take it to the extreme and

@@

However, the reality is quite the opposite. While people can be straightforward and appear ``cold'', they are also informal, friendly, and very caring (in ways that might surprise you).
With lab mates and colleagues, you will often work and go to lunch together, confide in each other, help each other navigate the academic journey, and often become lifelong friends.
With your professor(s), you can call them by their first name (\autoref{sec:address}), disagree with them and argue (and gain respect doing so), seek their help (even on personal matters), come to their houses for parties or gathering, and give them small thoughtful gifts that they put on their desks (\autoref{sec:gifts}).  
Many people maintain lifelong relationships with their professors and colleagues, staying in touch through cards, emails, and calls, even after their academic journey ends. %These connections are genuine and meaningful.

\begin{commentbox}[Vu:]
    My lab has various activities together (see \href{https://photos.app.goo.gl/LFtbqQUuznq9eiL7A}{here}). For example, we always have a Thanksgiving get-together at my house. Many faculty I know have similar activities with their lab members. 
  \end{commentbox}

>>>>

\section{Costly Gifts}\label{sec:gifts} In many countries, it is customary to give professors costly gifts (e.g., expensive liquors, jewelry, or even money), often during the holidays, to show respect and appreciation.  In the US, this is can be considered \emph{inappropriate} and discouraged.

@@

However, the reality is quite the opposite. While people can be straightforward and appear ``cold'', they are also informal, friendly, and very caring (in ways that might surprise you).
With lab mates and colleagues, you will often work and go to lunch together, confide in each other, help each other navigate the academic journey, and often become lifelong friends.
With your professor(s), you can call them by their first name (\autoref{sec:address}), disagree with them and argue (and gain respect doing so), seek their help (even on personal matters), come to their houses for parties or gathering (e.g., my lab always come to my house for \href{https://photos.app.goo.gl/LFtbqQUuznq9eiL7A}{Thanksgiving}), and give them small thoughtful gifts that they put on their desks (\autoref{sec:gifts}).  
Many people maintain lifelong relationships with their professors and colleagues, staying in touch through cards, emails, and visits, even after they nolonger work together.

\begin{commentbox}[Vu:]
    I maintain a close relationship with my former professors and mentors. When there is a new event in my life (or theirs), I often send them an email or call them, e.g., when I get married, have a new baby, new job, etc. When I was having issues at UNL and considering leaving, I talked to them. I don't think this bothers them a bit; I think they are actually interested in these ``dramas'' in my life and would be offended if I didn't come to them.

    I also visit my former professors when I am in their area. I meet Thang Bui (my MS adviser) at least once a year when I come back to Harrisburg to visit my parents. When Steph was in DC for a meeting, I invited her to Mason to give a talk on her work. I have also collaborated with them after I graduated e.g., I am working with Deepak on an NSF proposal on invariant generation.

    In short, while I am a bit closer to my former advisers and mentors than most people (e.g., I still keep in touch with my middle school teacher in Hawaii), it is always a good idea to maintain a good relationship with people who have helped or worked well with you. A simple, short email or text once in a while (e.g., a \emph{``Hi X, I heard you just got promoted ... Congrats!''}) would suffice. They will appreciate it and you never know when you might need their help.
